
% \bibliographystyle{plain}
\bibliographystyle{GBT7714-2005NLang_Upp}
% \bibliography{chap/references}
%& This .bbl file has been processed by fixbbl!
%& This .bbl file has been processed by fixbbl!
\begin{thebibliography}{148}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\expandafter\ifx\csname urlstyle\endcsname\relax
\providecommand{\doi}[1]{doi: #1}\else
\providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi

\bibitem{FroBot_iros}
Yi Y, Geng Z, Jianqing Z, et al. Design, modeling and control of a novel amphibious robot with dual-swing-legs propulsion mechanism[C]//Intelligent Robots and Systems (IROS), 2015 IEEE/RSJ International Conference on. IEEE, 2015: 559-566.

\bibitem{robotfish_BCF} 
Kopman V, Laut J, Acquaviva F, et al. Dynamic modeling of a robotic fish propelled by a compliant tail[J]. Oceanic Engineering, IEEE Journal of, 2015, 40(1): 209-221.

\bibitem{robotfish_MPF} 
Zhou C, Low K H. Locomotion planning of biomimetic robotic fish with multi-joint actuation[C]//Intelligent Robots and Systems, 2009. IROS 2009. IEEE/RSJ International Conference on. IEEE, 2009: 2132-2137.

\bibitem{model_MPF}
Sfakiotakis M, Fasoulas J, Gliva R. Dynamic modeling and experimental analysis of a two-ray undulatory fin robot[C]//Intelligent Robots and Systems (IROS), 2015 IEEE/RSJ International Conference on. IEEE, 2015: 339-346.

\bibitem{robotfish_BCFCN} 
苏玉民, 杨亮. 二维柔性摆动水翼水动力性能的数值分析[J]. 2012.

\bibitem{robotfish_Greece}
Sfakiotakis M, Kazakidi A, Evdaimon T, et al. Multi-arm robotic swimmer actuated by antagonistic SMA springs[C]//Intelligent Robots and Systems (IROS), 2015 IEEE/RSJ International Conference on. IEEE, 2015: 1540-1545.

\bibitem{attack_angle}
罗宾逊, 船舶工程, Robinson A, et al. 机翼理论[M]. 科学出版社, 1964.

\bibitem{anti_biaswheel}
苗英恺. 游龙板运动的力学分析[J]. 濮阳职业技术学院学报, 2009, 22(5): 159-160.

\bibitem{torque_cop}
CHibbeler R. Engineering Mechanics: Statics[J]. 2004.
\end{thebibliography}
